SimBio: a flexible and extensible Python package for systems modelling

### 2023-11-10 article.qmd
Mention numba backend in poincaré section
Change title

---
title: "SimBio: a static typing, modern Python package to simulate reaction networks"
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
---

@@

>>>>

---
title: "SimBio: a flexible and extensible Python package for systems modelling"
format:
  html:
    number-sections: true
    anchor-sections: true
  pdf:
    documentclass: scrartcl
    papersize: a4
    geometry:
        - margin=20mm
    pdf-engine: tectonic
    number-sections: true
    colorlinks: true
---

@@

Switching backends to `"numba"` can improve model runtime
on a factor upto x30 or more for big or long running models,
but incurs in a compile time penalty for the first run
which must be taken into account.
